\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-12-12 paper.tex
fix gramma errors

A preliminary version of this approach is presented in \cite{yang2020multi,yang2021multi}. That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, and incorporated the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives. However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance. As an extension of the previous works \cite{yang2020multi,yang2021multi}, we introduce reachability analysis and network flow to the security problem to find a balance between security and performance.}

@@

\new{Furthermore, we address the feasibility and optimality challenges. For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones.} These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams. The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another. This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in \cref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events. The cross-trajectory co-observation problem is transformed as a \new{Multi-Agent Pathfinding (MAPF)} problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.

@@

\noindent\myparagraph{Related research} The trajectory planning problem of MRS remains as a subject of intense study for many decades, and optimization is a common approach in such area. Optimization-based approaches are customizable to a varity of constraints (e.g. speed limit, avoiding obstacles) and task specifications (e.g. maximum surveillance coverage, minimal energy cost). In contrast to our work in \cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}. Several optimization techniques like mixed integer programs with quadratic terms (MIQP)~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity and to incorporate more complex non-convex constraints.

@@

% Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}. One typical approach involves computing an over-approximation of the reachable space for checking safety properities. Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric representation, such as zonotopes and ellipsoids, as a compact enclosure of the reachability sets. In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions. 
\new{Reachability analysis is essential for security and safety verification in cyber-physical systems (CPSs) \cite{gueguen2009safety, ding2020secure}, often involving an over-approximation of reachable space to verify safety properties. Geometric methods like zonotopes and ellipsoids are commonly used to enclose reachability sets compactly \cite{kurzhanski2000ellipsoidal, lakhal2019interval, maiga2015comprehensive}. For online safety assessments against cyber attacks, \cite{kwon2017reachability} computed reachable CPS states under attacks and compared them with a safe region based on state estimation. By incorporating an additional security measure that provides two secured states, the reachability region in our work is over-approximated using ellipsoids. This is inspired by the ellipsoidal \emph{heuristic sampling domain} in \cite{gammell2014informed} for the $\mathtt{RRT^*}$ algorithm to simplify the sampling region between start and goal locations. Ellipsoids are also used in other path-planning methods like Iterative Regional Inflation by Semidefinite programming (IRIS) \cite{deits2015computing, ray2022free} and the Safe Flight Corridor (SFC) \cite{liu2017planning, fan2024flying}. Differing from the reachability region that requires mapping all reachable states given several known states, the ellipsoids of IRIS and SFC focus on approximating the safe collision-free space rather than addressing security applications.}

@@

\noindent\myparagraph{Notation} 
In this paper, we use non-bold symbols like to denote single-agent states (e.g. $q_{ij}$) and scalers, while bold symbols represent aggregated states of single robot and multiple robots (e.g. $\vq$). }

@@

{\news Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimizing coverage, and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}). However, we consider the possibility of threats following the \emph{physical masquerade attack} model \cite{wardega2019resilience}, where a compromised insider (robot) masquerading as properly functioning agent, attempts to gain access to unauthorized locations without detection. The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE). These malicious deviations remain undetected as long as observations from uncompromised robots align with the motion plan. The corresponding security requirement can then be formally defined as:}
\begin{definition}\label{def:secured-plan}
  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
\end{definition}

@@

The update steps of the algorithm are then derived as \cite{Boyd2011}:
\begin{subequations}\label{eq:ADMMupdate}
	\begin{align}
		\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\label{eq:admm-mod-update-q}\\
		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \label{eq:z-update} \\
		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1}, \label{eq:u-update}
	\end{align}
\end{subequations}
where $\Pi_\mathcal{Z}$ is the new projection function to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
\begin{equation}\label{eq:primal-residual}
	\vr^{k}=D(\vq^{k+1})-\vz^{k+1}.
\end{equation}
Checking the primal residuals alongside the dual residuals 
\begin{equation}\label{eq:dual-residual}
	\vs^{k}=-\rho(\vz^{k}-\vz^{k-1})
\end{equation}
after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residuals remain large after a fixed number of iterations.
{\news
\begin{remark}
In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver such as \emph{fmincon}~\cite{MATLAB:fmincon}. The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numericall differentiation). At the same time, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
\end{remark}
}
% \rtron{Maybe state here that (9a) is solved iteratively, while (9b) and (9c) are closed-form.}

@@

% We write the function for the constraint as:
\begin{constraint}[Co-observation constraint]\label{constraint:coobservation}
\begin{align}
D(\vq) &= \overrightarrow{q_{aj}q_{bj}}, \label{eq:coobservation_constraint}\\
  \sZ &= \{\vz \mid \norm{\vz} \leq d_{max} \},\\
   \Pi_\sZ(z) & = \begin{cases}
d_{max}\frac{\vz}{\norm{\vz}} &\text{if } \norm{\vz} > d_{max},\\
\vz	& otherwise,
\end{cases}
\end{align}
where $a,b$ are the indices of the pair of agents required for a mutual inspection, \new{$d_{max}$ is the maximum distance between a pair of robots that the secure can be ensured through co-observation.}
\end{constraint}
The locations $q_{aj}$ and $q_{bj}$ where the co-observation is performed are computed as part of the optimization.

@@

\new{In this section, we define \emph{ellipsoidal reachability regions} with respect to a pair of locations along a trajectory. We then use the ellipsoids to introduce various reachability constraints with respect to other geometric entities, such as points, lines, line segments, and polygons. These constraints, combined with the co-observation constraint~\ref{constraint:coobservation}, form the basis of the secured ADMM planning presented in \cref{chapter:ADMM review}.
}
% In this section, we define \emph{ellipsoidal reachability regions} based on pairs of co-observation locations on a trajectory, and a transformation of such region in axis-aligned form. Different types of reachability constraints (between an ellipsoid and different geometric entities such as a point, line, line segment, and polygon) alongside their projections, and differentials are introduced in subsequent sections. Together with the co-observation constraint~\ref{constraint:coobservation}, these will be used in the ADMM formulation of \cref{chapter:ADMM review} to provide security for all observed and unobservered periods.
%The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
{\news
\begin{definition}\label{sec:ellipsoidal definition}
Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$. The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
	% The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \new{free configuration space} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}. 
\end{definition}

@@

    \caption{\news (\ref{fig:EllipseConstraintExample}) The black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations where the robot are expected at given time $t_1$ and $t_2$, dashed lines show a possible trajectory of a compromised robot during the unobserved period. The axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively. 
    (\ref{fig:Ellipse-to-point}) For point-ellipsoid constraint, $q_{avoid}$ is projected to the areas outside the ellipsoid to $q_{p}$. 
    (\ref{fig:Ellipse-to-plane}) For plane-ellipsoid constraint, the projection is simplified to the point-ellipse constraint that projects point $p_{L}$ outside the ellipse to $p_{t}$.
    (\ref{fig:Ellipse-to-safezone}) For convec-polygon-ellipsoid constraint, the projection is either a plane-ellipse constraint $D_{1}$ (for the red region) or a point-ellipse constraint $D_{2}$ (for the brown region).}
    \label{fig:Reachability_full}
  \end{figure}

@@

For every $\Eframe \cL(\Eframe{q})$, there exist two planes that are both parallel to $\cL$ and tangential to the ellipse (i.e. resulting in a unique intersection point \cref{fig:Ellipse-to-plane}), $\cL_1^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} = - d_{\cE t} \}$. The intersection point can be written as:
\begin{equation}
    p^\cE_{t_{1}} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{t_{2}} = -  p^\cE_{t_{1}},
\end{equation}
where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be treated as a distance between the tangent plane $\cL_1^\cE$ (or $\cL_2^\cE$) and the origin (i.e., the center of the ellipse $\cE$). The concept of \emph{tangent interpolation point}s is introduced to characterize the relationship between the plane and the ellipsoid.

@@

% \begin{constraint}[Line-segment-ellipsoid reachability constraint]
% \begin{align}
% D(\vq) &=  \begin{cases}
% D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
% D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
% D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
% \end{cases} \label{eq:segment_ellipsoid_constraint}\\
%   \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
%    \Pi_\sZ(\vz) & = 0, 
% \end{align}
% \end{constraint}
% where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}. with respect to frame $\Eframe {\cL}$.
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint}
{\news  
The reachability constraints for a convex polygon is treated as a union of reachability constraints for aeach indivisual segments that define the hyperplane. We define
\begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
\begin{align}
D(\vq) &= \bmat{D_{seg1}(\vq)\\D_{seg2}(\vq)\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{seg}$ are the constraint functions for all line segments used to define the convex polygon region. 
For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:
\begin{equation}
\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
\end{equation}
When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}. Otherwise (i.e. brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.

@@

We employ the \new{Attack-Proof MAPF (APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}). This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task. Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions. Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions. {\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space. In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids. Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated. For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}

@@

\subsection{Rapidly-exploring Random Trees}
To find edges between different nominal trajectories, we use the \rrtstar{}~\cite{karaman2010incremental} algorithm to find paths from a waypoint on one trajectory to multiple destination points (i.e., reference trajectories of other sub-teams, in our method). As a optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and points in the free configuration space, organized as a tree. We assume that the generated paths can be traveled in both directions (this is used later in our analysis). 
Key function from \rrtstar{} is used during constructions of the checkpoint graph, specifically
{\news\begin{description}
\item[$\texttt{Cost}(v)$] This function returns a total travel distance to the unique path from the initial position to $v$. 
\end{description}}

@@

Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ correspond to a security checkpoint $\union_p V_p$. The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur {\news while switching trajectories}.  
%\end{remark}

@@

\begin{remark}
Note that we assign fixed roles to robots for convenience in explaining the multi-flow formulation. In practice, after a cross-trajectory robot joins a team, it is considered interchangable and could switch roles with the reference robot of that trajectory. % (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation).
\end{remark}

>>>>

A preliminary version of this approach is presented in \cite{yang2020multi,yang2021multi}. That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration space, and incorporated the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives. However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance. As an extension of the previous works \cite{yang2020multi,yang2021multi}, we introduce reachability analysis and network flow to the security problem to find a balance between security and performance.}

@@

\new{Furthermore, we address the feasibility and optimality challenges. For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and form them into \emph{sub-teams} with the original ones.} These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams. The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another. This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in \cref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events. The cross-trajectory co-observation problem is transformed as a \new{Multi-Agent Pathfinding (MAPF)} problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.

@@

\noindent\myparagraph{Related research} The trajectory planning problem of MRS remains as a subject of intense study for many decades, and optimization is a common approach in such areas. Optimization-based approaches are customizable to a variety of constraints (e.g. speed limit, avoiding obstacles) and task specifications (e.g. maximum surveillance coverage, minimal energy cost). In contrast to our work in \cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}. Several optimization techniques like mixed integer programs with quadratic terms (MIQP)~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity and to incorporate more complex non-convex constraints.

@@

% Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}. One typical approach involves computing an over-approximation of the reachable space for checking safety properities. Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric representation, such as zonotopes and ellipsoids, as a compact enclosure of the reachability sets. In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions. 
\new{Reachability analysis is essential for security and safety verification in cyber-physical systems (CPSs) \cite{gueguen2009safety, ding2020secure}, often involving an over-approximation of reachable space to verify safety properties. Geometric methods like zonotopes and ellipsoids are commonly used to enclose reachability sets compactly \cite{kurzhanski2000ellipsoidal, lakhal2019interval, maiga2015comprehensive}. For online safety assessments against cyber attacks, \cite{kwon2017reachability} compute reachable CPS states under attacks and compared them with a safe region based on state estimation. By incorporating an additional security measure that provides two secured states, the reachability region in our work is over-approximated using ellipsoids. This is inspired by the ellipsoidal \emph{heuristic sampling domain} in \cite{gammell2014informed} for the $\mathtt{RRT^*}$ algorithm to simplify the sampling region between start and goal locations. Ellipsoids are also used in other path-planning methods like Iterative Regional Inflation by Semidefinite programming (IRIS) \cite{deits2015computing, ray2022free} and the Safe Flight Corridor (SFC) \cite{liu2017planning, fan2024flying}. Differing from the reachability region that requires mapping all reachable states given several known states, the ellipsoids of IRIS and SFC focus on approximating the safe collision-free space rather than addressing security applications.}

@@

\noindent\myparagraph{Notation} 
In this paper, we use non-bold symbols to denote single-agent states (e.g. $q_{ij}$) and scalars, and bold symbols to represent aggregated states of single robot and multiple robots (e.g. $\vq$). }

@@

{\news Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimize coverage, and minimize reconstruction uncertainty (\cref{fig:SecurityBreak}). However, we consider the possibility of threats following the \emph{physical masquerade attack} model \cite{wardega2019resilience}, where a compromised insider (robot) masquerading as a properly functioning agent, attempts to gain access to unauthorized locations without detection. The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE). These malicious deviations remain undetected as long as observations from uncompromised robots align with the motion plan. The corresponding security requirement can then be formally defined as:}
\begin{definition}\label{def:secured-plan}
  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
\end{definition}

@@

The update steps of the algorithm are then derived as \cite{Boyd2011}:
\begin{subequations}\label{eq:ADMMupdate}
	\begin{align}
		\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\label{eq:admm-mod-update-q}\\
		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \label{eq:z-update} \\
		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1}, \label{eq:u-update}
	\end{align}
\end{subequations}
where $\Pi_\mathcal{Z}$ is the new projection function to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
\begin{equation}\label{eq:primal-residual}
	\vr^{k}=D(\vq^{k+1})-\vz^{k+1}.
\end{equation}
Checking the primal residuals alongside the dual residuals 
\begin{equation}\label{eq:dual-residual}
	\vs^{k}=-\rho(\vz^{k}-\vz^{k-1})
\end{equation}
after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residuals remain large after a fixed number of iterations.
{\news
\begin{remark}
In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver such as \emph{fmincon}~\cite{MATLAB:fmincon}. The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numerical differentiation). At the same time, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
\end{remark}
}
% \rtron{Maybe state here that (9a) is solved iteratively, while (9b) and (9c) are closed-form.}

@@

% We write the function for the constraint as:
\begin{constraint}[Co-observation constraint]\label{constraint:coobservation}
\begin{align}
D(\vq) &= \overrightarrow{q_{aj}q_{bj}}, \label{eq:coobservation_constraint}\\
  \sZ &= \{\vz \mid \norm{\vz} \leq d_{max} \},\\
   \Pi_\sZ(z) & = \begin{cases}
d_{max}\frac{\vz}{\norm{\vz}} &\text{if } \norm{\vz} > d_{max},\\
\vz	& otherwise,
\end{cases}
\end{align}
where $a,b$ are the indices of the pair of agents required for a mutual inspection, \new{$d_{max}$ is the maximum distance between a pair of robots that the security can be ensured through co-observation.}
\end{constraint}
The locations $q_{aj}$ and $q_{bj}$ where the co-observation is performed are computed as part of the optimization.

@@

\new{In this section, we define \emph{ellipsoidal reachability regions} with respect to a pair of locations along a trajectory. We then use the ellipsoids to introduce various reachability constraints with respect to other geometric entities, such as points, lines, line segments, and polygons. These constraints, combined with the co-observation constraint~\ref{constraint:coobservation}, form the basis of the secured ADMM planning is presented in \cref{chapter:ADMM review}.
}
% In this section, we define \emph{ellipsoidal reachability regions} based on pairs of co-observation locations on a trajectory, and a transformation of such region in axis-aligned form. Different types of reachability constraints (between an ellipsoid and different geometric entities such as a point, line, line segment, and polygon) alongside their projections, and differentials are introduced in subsequent sections. Together with the co-observation constraint~\ref{constraint:coobservation}, these will be used in the ADMM formulation of \cref{chapter:ADMM review} to provide security for all observed and unobservered periods.
%The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
{\news
\begin{definition}\label{sec:ellipsoidal definition}
Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$. The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
	% The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \new{free configuration space} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}. 
\end{definition}

@@

    \caption{\news (\ref{fig:EllipseConstraintExample}) The black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations where the robots are expected at given times $t_1$ and $t_2$, dashed lines show a possible trajectory of a compromised robot during the unobserved period. The axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively. 
    (\ref{fig:Ellipse-to-point}) For point-ellipsoid constraint, $q_{avoid}$ is projected to the areas outside the ellipsoid to $q_{p}$. 
    (\ref{fig:Ellipse-to-plane}) For plane-ellipsoid constraint, the projection is simplified to the point-ellipse constraint that projects point $p_{L}$ outside the ellipse to $p_{t}$.
    (\ref{fig:Ellipse-to-safezone}) For convex-polygon-ellipsoid constraint, the projection is either a plane-ellipse constraint $D_{1}$ (for the red region) or a point-ellipse constraint $D_{2}$ (for the brown region).}
    \label{fig:Reachability_full}
  \end{figure}

@@

For every $\Eframe \cL(\Eframe{q})$, there exist two planes that are both parallel to $\cL$ and tangential to the ellipse (i.e. resulting in a unique intersection point \cref{fig:Ellipse-to-plane}), $\cL_1^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} = - d_{\cE t} \}$. The intersection point can be written as:
\begin{equation}
    p^\cE_{t_{1}} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{t_{2}} = -  p^\cE_{t_{1}},
\end{equation}
where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be treated as a distance between the tangent plane $\cL_1^\cE$ (or $\cL_2^\cE$) and the origin (i.e., the center of the ellipse $\cE$). The concept of \emph{tangent interpolation point}s are introduced to characterize the relationship between the plane and the ellipsoid.

@@

% \begin{constraint}[Line-segment-ellipsoid reachability constraint]
% \begin{align}
% D(\vq) &=  \begin{cases}
% D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
% D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
% D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
% \end{cases} \label{eq:segment_ellipsoid_constraint}\\
%   \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
%    \Pi_\sZ(\vz) & = 0, 
% \end{align}
% \end{constraint}
% where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}. with respect to frame $\Eframe {\cL}$.
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint}
{\news  
The reachability constraints for a convex polygon is treated as a union of reachability constraints for each individual segments that define the hyperplane. We define
\begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
\begin{align}
D(\vq) &= \bmat{D_{seg1}(\vq)\\D_{seg2}(\vq)\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
   \Pi_\sZ(\vz) & = 0, 
\end{align}
\end{constraint}
where $D_{seg}$ are the constraint functions for all line segments that define the convex polygon region. 
For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:
\begin{equation}
\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
\end{equation}
When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}. Otherwise (i.e. brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.

@@

We employ the \new{Attack-Proof MAPF (APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}). This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task. Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions. Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions. {\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space. In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids. Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated. For instance, in this scenario, we deploy a security camera as an additional security measure to observe agent 3 at time $8$ to ensure security.}

@@

\subsection{Rapidly-exploring Random Trees}
To find edges between different nominal trajectories, we use the \rrtstar{}~\cite{karaman2010incremental} algorithm to find paths from a waypoint on one trajectory to multiple destination points (i.e., reference trajectories of other sub-teams, in our method). As an optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and points in the free configuration space, organized as a tree. We assume that the generated paths can be traveled in both directions (this is used later in our analysis). 
Key function from \rrtstar{} is used during the construction of the checkpoint graph, specifically
{\news\begin{description}
\item[$\texttt{Cost}(v)$] This function returns a total travel distance to the unique path from the initial position to $v$. 
\end{description}}

@@

Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ corresponds to a security checkpoint $\union_p V_p$. The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur {\news while switching trajectories}.  
%\end{remark}

@@

\begin{remark}
Note that we assign fixed roles to robots for convenience in explaining the multi-flow formulation. In practice, after a cross-trajectory robot joins a team, it is considered interchangeable and could switch roles with the reference robot of that trajectory. % (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation).
\end{remark}
